Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Updated this table

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, interface or enumeration, including its declaration.
  \item \textbf{Partial Method:} A clone that spans a method partially, optionally including its declaration.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields:} A clone that spans a combination of fields and other things, like methods.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
  \item \textbf{Other:} Anything that does not match with above stated categories.
\end{enumerate}

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
SEVERALMETHODS          & 9.077            & 26,41               \\ \hline
FULLCLASS               & 198             & 0,58                \\ \hline
FULLENUM                & 4               & 0,01                \\ \hline
FULLMETHOD              & 554             & 1,61                \\ \hline
INCLUDESFIELDS          & 1.150            & 3,35                \\ \hline
HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
HASENUMDECLARATION      & 47              & 0,14                \\ \hline
FULLINTERFACE           & 6               & 0,02                \\ \hline
HASENUMFIELDS           & 52              & 0,15                \\ \hline
PARTIALMETHOD           & 19.263           & 56,05               \\ \hline
ONLYFIELDS              & 565             & 1,64                \\ \hline
OTHER                   & 2.996            & 8,72                \\ \hline
\end{tabular}
\end{center}
\end{table}
%TODO: Finish text and add measurements.

>>>>

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Class/Interface/Enumeration/Constructor:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
  \item \textbf{Other:} Anything that does not match with above stated categories.
\end{enumerate}

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents}
  \bigskip
\begin{tabular}{|l|l|l|}
  \hline
  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
  Partial Method                                                           & 19.264          & 56,07               \\ \hline
  Several Methods                                                          & 9.076           & 26,41               \\ \hline
  Includes Constructor                                                     & 1.528           & 4,45                \\ \hline
  Includes Field                                                           & 1.149           & 3,34                \\ \hline
  Partial Constructor                                                      & 1.098           & 3,20                \\ \hline
  Only Fields                                                              & 565             & 1,64                \\ \hline
  Full Method                                                              & 554             & 1,61                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1,30                \\ \hline
  Other                                                                    & 369             & 1,07                \\ \hline
  Full Class                                                               & 192             & 0,56                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0,15                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0,14                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0,03                \\ \hline
  Full Interface                                                           & 6               & 0,02                \\ \hline
  Full Enumeration                                                         & 4               & 0,01                \\ \hline
  Full Constructor                                                         & 1               & 0,00                \\ \hline
\end{tabular}
\end{center}
\end{table}
%TODO: Finish text and add measurements.
